Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
centering column headers
parameters -> octagons

\begin{table}[!h]
	\centering
\begin{tabular}{|l|r|r|r|r|r|} \hline
	Benchmark & \textbf{S} & \textbf{G} & \textbf{PF} & \textbf{G+PF} &
	\textbf{DIS} \\ \hline
	\input{table_time.tex} \hline
\end{tabular}
\caption{Execution time for each technique, expressed in seconds}
\label{tab:time}
\end{table}

@@

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields greater invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator.
% DM Ici on pourrait citer Monniaux+Le Guen si c'etait publie!
The Octagon domain appears to be much better than intervals.
\JH{Commenter les resultats}

>>>>

\begin{table}[!h]
	\centering
\begin{tabular}{|l|r|r|r|r|r|} \hline
	\multicolumn{1}{|c|}{Benchmark} &
        \multicolumn{1}{c|}{\textbf{S}} &
        \multicolumn{1}{c|}{\textbf{G}} &
        \multicolumn{1}{c|}{\textbf{PF}} &
        \multicolumn{1}{c|}{\textbf{G+PF}} &
	\multicolumn{1}{c|}{\textbf{DIS}} \\ \hline
	\input{table_time.tex} \hline
\end{tabular}
\caption{Execution time for each technique, expressed in seconds}
\label{tab:time}
\end{table}

@@

Statistically, the domain of convex polyhedra gives the better results, but
commonly yields greater invariants than the domains of octagons/intervals;
this is a known weakness of its widening operator.
\DM{Ici on pourrait citer Monniaux+Le Guen si c'etait publie!}
The Octagon domain appears to be much better than intervals; this is
unsurprising since in most programs and libraries, bounds on loop indices are
non constant: they depend on some parameters (array sizes etc.).
\JH{Commenter les resultats}
